### 2021-06-10 paper/report.tex
Add paragraph on schools.

The effects of various mechanisms can be disentangled due to the distinct temporal
variation in the drivers of the pandemic. Next to the stringency index, the three lines
in Figure~\ref{fig:stringency_index} summarize how contact reductions, increased hygiene
regulations, and seasonality evolved since early September for each of the three broad
contact networks. For example, a value of 0.75 for the work multiplier means that if the
environment was the same as in September (levels of infection rates, no rapid tests or
vaccinations, only the wildtype virus present), infections at the workplace would be
reduced by 25\%. The lines show the product of the effect of contact reductions,
increased hygiene regulations, and seasonality. See Appendix~\comment[id=HM]{Reference}
for separate plots of the three factors. Two aspects are particularly interesting.
First, all lines broadly follow the stringency index and they would do so even more if
we left out seasonality and school vacations (roughly the last two weeks of October, two
weeks each around Christmas and Easter, and some days in late May). Second, the most
stringent regulations are associated with the period of strong decreases in new
infections between late December 2020 and mid-February 2021. The reversal of the trend
is associated with he spread of the B.1.1.7 variant. The steep drop in recorded cases
during May 2021 is associated with at least weekly rapid tests to around 42~percent of
the population, a vaccination rate that rose from 28\% to 43\%, and mostly seasonality
impacting a fall in the relative infectiousness of contacts outside of work and school.

@@

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operaton was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding school starting at Easter, a point where rapid tests had become widely available.

In light of the large negative effects school closures have on children and
parents\comment[id=HM]{need to cite a couple of poor learning outcomes / mental health
papers. There must be well-published ones}---and in particular on those with low
socio-economic status---the results in

>>>>

The effects of various mechanisms can be disentangled due to the distinct temporal
variation in the drivers of the pandemic. Next to the stringency index, the three lines
in Figure~\ref{fig:stringency_index} summarize how contact reductions, increased hygiene
regulations, and seasonality evolved since early September for each of the three broad
contact networks. For example, a value of 0.75 for the work multiplier means that if the
environment was the same as in September (levels of infection rates, no rapid tests or
vaccinations, only the wildtype virus present), infections at the workplace would be
reduced by 25\%. The lines show the product of the effect of contact reductions,
increased hygiene regulations, and seasonality. See Appendix~\ref{subsec:policies} for
separate plots of the three factors. Two aspects are particularly interesting. First, all
lines broadly follow the stringency index and they would do so even more if we left out
seasonality and school vacations (roughly the last two weeks of October, two weeks each
around Christmas and Easter, and some days in late May). Second, the most stringent
regulations are associated with the period of strong decreases in new infections between
late December 2020 and mid-February 2021. The reversal of the trend is associated with he
spread of the B.1.1.7 variant. The steep drop in recorded cases during May 2021 is
associated with at least weekly rapid tests to around 42~percent of the population, a
vaccination rate that rose from 28\% to 43\%, and mostly seasonality impacting a fall in
the relative infectiousness of contacts outside of work and school.

@@

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operaton was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies
regarding school starting at Easter, at which point rapid tests had become widely
available. We estimate the realized scenario to have essentially the same effect as a
situation with closed schools. Under fully opened schools with mandatory tests, total
infections would have been 7\% higher; this number rises to 20\% without tests. These
effect sizes are broadly in line with emprical studies, e.g., \citet{Vlachos2021}
\comment[id=HM]{\url{https://www.pnas.org/content/118/9/e2020834118}}
\comment[id=HM]{Need a back-of the envelope calculation} To use another metric, the
effective weekly reproduction number differs by $0.017$ and $0.045$, respectively. In
light of the large negative effects school closures have on children and
parents\comment[id=HM]{need to cite a couple of poor learning outcomes / mental health
papers. There must be well-published ones}---and in particular on those with low
socio-economic status---these results in conjunction with hindsight bias suggest that
opening schools combined with a testing strategy would have been beneficial. In other
situations, and particular when no test strategy is available, trade-offs may well be
different.
